|

### 2021-05-12 04-Chp-CPRD-Analysis.Rmd
End of day: -3964

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

<!-- Note: If protocol was written by Venexia, how do I reference this? -->

@@

<!--- TODO this table doesn't exist anywhere as it has been cut off the bottom of Table 1 --->

@@

Of the `r comma(attrition[1,1])` participants included in our extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of 11,091,437 <!--- TODO make this reactive! ---> patient years at risk.

@@

@@

<!--- TODO In my most recent discussion with --->

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
options(scipen = 99)
knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

<!-- NOTE If protocol was written by Venexia, how do I reference this? -->

@@

@@

Of the `r comma(attrition[1,1])` participants included in our extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` <!--- TODO make this reactive! ---> patient years at risk.

@@

<!--- TODO Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? --->

<!----------------------------------------------------------------------------->
(ref:cprdSSA-caption) Participants who stopped, switched or added treatements by initial treatment type

(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type

```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

@@

<!--- TODO In my most recent discussion with supervisors, I discussed that a long term RCT isn't encouraged by the results --->
